---
title: "Heart Disease"
output: html_document
date: "2023-11-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

**Data Description**

Personal Key Indicators of Heart Disease
2020 annual CDC survey data of 400k adults related to their health status
Target - HeartDisease - Yes / No
Features
BMI - Normal weight (18.5 <= BMI < 25.0)
Smoking - Have you smoked at least 100 cigarettes in your entire life (approx. 5 packs)?
AlcoholDrinking - Do you have more than 14 drinks of alcohol (men) or more than 7 (women) in a week?
Stroke - Did you have a stroke?
PhysicalHealth - For how many days during the past 30 days was your physical health not good?
MentalHealth - For how many days during the past 30 days was your mental health not good?
DiffWalking - Do you have serious difficulty walking or climbing stairs?
Sex
AgeCategory
Race
Diabetic
PhysicalActivity - Have you played any sports (running, biking, etc.) in the past month?
GenHealth - How can you define your general health?
SleepTime - How many hours on average do you sleep?
Asthma
KidneyDisease
SkinCancer

```{r}
heart = read.csv('/Users/varunthallapelly/Desktop/One last time/sanjay/heart_2022_no_nans.csv')
hdp = heart
```

**Cheching null values**

```{r}
colSums(is.na(hdp))
```

There are No null values in the dataset

**Checking duplicate data**

```{r}
sum(duplicated(hdp))
```

There are few duplicate rows in the dataset

**Removing Duplicated rows from the dataset**

```{r}
hdp_unique = unique(hdp)
sum(duplicated(hdp_unique))
```

```{r}
dim(hdp_unique) #Dimension of the data
```

there are 40 variables and 246013 Observations

```{r}

```

